Examination of shapes! (homework exam)

### 2016-02-22 geometricAlgorithms/homeworkExam/homeworkExam.tex
I think I finished the recursive function

\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
\begin{algorithmic}
	\State Sort all line segment $s \in S$ end points $p$ based on
		$y$ coordinate.
		$p$ should have a reference to its coorisponding point (ie the start
		point has a reference to the end point and vice versa). The resulting
		collection is called $E_{sorted}$
	\For{point$\in E_{sorted}$}
		\State
		\If{begin point} insert in State. On inserted point calculate
		if there is a crossing if so insert in $E_{sorted}$.
		\EndIf
		\If{end point} remove begin point from state.
		\EndIf
		\If{Crossing point} add to result.
		\EndIf
	\EndFor
\end{algorithmic}

\subsection{Why takes this algorithm linear time}
\section{Red and blue lines}
\section{Polygon cut}
\section{Diagonal polygon cut}
\end{empfile}
\end{document}

>>>>

\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
%TODO: should we find the side?

\begin{algorithmic}
	\Function{findxySilhouette}{$v_{start}, v_{current}, S_{result}$}
	\If{$v_{start}$ is equal to $v_{current}$} 
		\State \Return $S_{result}$
	\EndIf
	\State
	$v_{next} \gets Origin(Next(IncidentEdge(v_{current})))$
	\State
	\Return \Call{findxySilhoeutte}{
		$v_{start}, v_{next}, S_{result} \cup v_{current}$
	}
	\EndFunction
	\Function{findxySilAlgoirthm}{$v_{start}$}
	\Comment{Helper function to suffice the contract (init work)}
	\State \Return
	\Call{findxySilhoeutte}{
		$v_{start}, Origin(Next(IncidentEdge(v_{start}))), Seq(v_{start})$
	}
	\Comment{The $Seq$ just makes an arbitrary sequence with constand append time}
	\EndFunction
	\State 
\end{algorithmic}

Because the Polyhedron $P$ is convex (so no weird dents), and
the initial vertex $v_{start}$ was already on the boundry this
alogrithm is correct.
In class we used marker bits but its simpler to just pass the
starting point, less chance to shoot yourself in the foot with
mutable state.

\subsection{Why takes this algorithm linear time}
Because all operations are linear or faster. In fact the slowest
operation, the recursive step is in itself linear. It is gauranteed to stop
as long as it is passed a cycle.

\section{Red and blue lines}
\subsection{The status structure}
A binary tree sorted on the x axis.
\subsection{Initialization}
\subsection{Distinguish the events and describe for each event how its handled}
\subsection{Analyze the time}
\section{Polygon cut}
\section{Diagonal polygon cut}
\end{empfile}
\end{document}
